---
title: "Relationship between mles per gallon and transmission type"
author: "Gaurav Bansal"
date: "Saturday, July 26, 2014"
output: pdf_document
---
Executive Summary
---

Through stepwise model selection through minimizing AIC, the output model turned out to be mpg ~
as.factor(cyl) + hp + wt + as.factor(am). However, performing ANOVA anlysis to compare the above model
with and without the am variable showed that such two models are likely to be similiar. A Shapiro-Wilk
test of normality over the residues the above model failed to reject the null hypothesis, validating the anova analysis.Therefore, basing on all the studies, the conclusions are: 1. with the given data, the manual and automatic transmission types do not significantly impact the MPG; 2. with the given data, holding all other variables constant, vehicle of manual transmission have 1.81 increase in MPG compared to vehicle of automatic transmission.

```{r, echo=TRUE}
#loading the data
data("mtcars")
summary(mtcars)
#changing the values of factor varables to factors
mtcars$cyl<- as.factor(mtcars$cyl)
mtcars$vs<- as.factor(mtcars$vs)
mtcars$am<- as.factor(mtcars$am)
mtcars$gear<- as.factor(mtcars$gear)
mtcars$carb<- as.factor(mtcars$carb)
```

Fit the model taking all factors and then find AIC, the one having the lowest AIC will be the best fit model

```{r, echo=TRUE}
fit <- lm(mpg~.,mtcars)
library("MASS")
x <- stepAIC(fit)
```

The model with cyl, hp, wt, am is the best fit model, so let us find the summary of this model, wether the values are significant or not

```{r, echo=TRUE}

fit1 <- lm(mpg~cyl+hp+wt+am,mtcars)
summary(fit1)
```

After fitting the variable the p-value for AM is found to be 0.20646 which is not significant and we fail to reject the null hpothesis

```{r, echo=TRUE}

fit1 <- lm(mpg~cyl+hp+wt+am,mtcars)
summary(fit1)
```

```{r, echo=TRUE}
#Also, let us test the anova of two models, one with am and one without am
fit1 <- lm(mpg~cyl+hp+wt+am,mtcars)
fit2 <- lm(mpg~cyl+hp+wt,mtcars)
anova(fit1,fit2)
```

P-value is 0.21 so we fail to reject the null hypothesis, these both the models are similar

```{r, echo=TRUE}
#test for normality of residues
shapiro.test(fit1$residuals)
```

P-value = 0.45, fail to reject the null. So the residues are likely to follow a normal distribution. So our anova test is likely to be valid.

Apendix
-----
```{r, echo=TRUE}
par(mfrow = c(2, 2))
plot(fit1)
```
